Environmental Dependence of the Structures of Massive Central Galaxies at $z=0.4$ ....... or ... A Detection of the Enviromental Dependence of The Stellar Halos of Massive Galaxies

### 2017-03-14 draft/ms_v2.tex
New draft

    The Subaru Strategic Program (SSP, \addref) makes use of the new prime-focus camera,
    the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 8.2-m Subaru telescope at 
    Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover $\sim 1400$ deg$^2$ in 5
    broad bands (\textit{g r i z Y}) to a limting depth of $r \sim 26$ mag in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    $\sim 100$square of degree in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

@@

The full details of the HSC data processing can be found in \citet{BoschInPrep} and are briefly summarized here. The HSC SSP data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large 
    Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC. 
    \texttt{hscPipe} first performs a number of tasks at the single exposure level 
    (bias subtraction, flat fielding, background modeling, object detection and 
    measurements). Astrometric and photometric calibration is performed at the single exposure level. \texttt{hscPipe} then warps different exposures on to a common
    World Coordinate System (WCS) and combines them into coadded images. At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
    photometric calibration using stars that are common among between exposures.

    The pixel scale of the combined images is $0.168^{\arcsec}$. Photometric calibration is based on data from the Panoramic Survey Telescope 
    and Rapid Response System (Pan-STARRS) 1 imaging survey 
    (\citealt{Schlafly2012}, \citealt{Tonry2012}, \citealt{Magnier2013}). 
    To achieve consistent deblending and photometry across all bands, \texttt{hscPipe} 
    performs multi-band post-processing at the coadd level. First, \texttt{hscPipe} performs object detection on coadd images
    in each band independently and for each source records the flux peak and the above-threshold region (referred as 
    a ``footprint''). Next, ``footprints'' and peaks from different bands are merged together before performing deblending and measurements. Finally, \texttt{hscPipe} selects a ``reference band'' for each object based on the 
    $S/N$ in different bands (for most galaxies in this work, the reference band is the $i$-band). 
    After fixing the centroids, shape, and other non-amplitude parameters of each 
    object in this reference catalog, \texttt{hscPipe} perform forced photometry 
    on the coadd image in each band. This forced photometry approach is optimized to yield accurate galaxy colors.

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach that is similar to SDSS (\ref{}) (Bosch\etal~in prep.~). However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which means that it can be used to accurately measure both the \textit{fluxes and colors of galaxies}. The HSC \cmodel{} algorithm fits the flux distribution of each object using a combination of a de~Vaucouleur and 
    an exponential component and accounts for the PSF. The performance of this algorithm has been testing using synthetic objects (Huang\etal~in prep.~) and 
    the results indicate that, generally speaking, the HSC \cmodel{} photometry is 
    accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of massive ETGs with extended stellar distributions. This problem indicates an intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles with extremely extended outskirts, a problem that is exacerbated at the depth of 
    the HSC survey. In addition, at the depth of the HSC survey, accurate deblending in the vicinity of large ETGs where satellites and background galaxies often blend with the low surface brightness stellar envelope is a challenign problem. The deblending method implemented by the \texttt{hscPipe} currently tends to 
    ``over-deblend'' the outskirts of bright galaxies and leads to un under-estimation of the the total flux of massive ETGs (more discussion in 
    Bosch\etal~in prep.~).  For these reasons, our results will be based on custom developed code to measure the luminosities and stellar masses of massive galaxies. We use the HSC \texttt{hscPipe} photometry for two purposes: 1) to perform a first broad sample selection, and 2) for galaxy colors. \alexie{Shouldn't we be using the aperture photometry here ???? Are we doing teh right thing here?? Please check. Need a simple sanity check to show that the resutls are robust. Check using your own color estimates?}.

@@

    \alexie{Try to be more succinct and improve the logical flow in sections 2.3, 2.4, and 2.5. Readers don't care about the process! You should be able to trim these sections.}

    \alexie{We never say anything about Spirals? Are all galaxies in this selection early types? Are there any extra morphology cuts? We need to mention this somewhere.}

    \update{
    We begin by using a broad luminosity cut to select an initial sample of massive galaxies at $z < 0.5$
    from the HSC photometric catalog.} Based on Leauthaud\etal~(2016), galaxies with \logms{}$\geq 11.5$ have 
    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. We therefore select our initla smaple to be brighter than  $i_{\mathrm{HSC, cModel}} \leq 21.5$ 
    \footnote{We neglect the insignificant differences between the response curves of
    SDSS-$i$ and HSC-$i$ filters} and also limit our sample to regions that have reached the required depth of the \texttt{WIDE} survey in all 
    five bands. 
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

    We further select extended objects with no deblending errors, with well defined 
    centroids, and with \texttt{cModel} magnitudes in all five bands. 
    After removing objects that have pixels affected by saturation, cosmic-rays, or 
    other optical artefact \footnote{each criterion removes less than 8\% of the entire
    sample} \alexie{Actually, 8 percent is not small if we want to condsider the number densities. Let's re-evaulate the impact of these cuts for the 16B data with FDFC}. This sample corresponds to 1760845 galaxies and will be referred as \texttt{hscPho}.

    %% Saved as "dr1_wide_galaxy_hscPho.fits"

    We limit our study to the very high mass end where a majority of galaxies have either a  spectroscopic redshift or a robust 
    red-sequence photo-$z$ from the \redm{} catalog (see Section \ref{ssec:redmapper}).  
    We match the \texttt{hscPho} sample with a spec-$z$ catalog 
    compiled by the HSC team\footnote{It is created by matching HSC objects with all publicly available spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). The spec-z quality flag from different catalogs 
    are homogenized into a single flag that indicates whether the redshift is secure (\ref{} Cite a paper from the photo team where this is described?). Only galaxies with secure spec-$z$s are used in this work \alexie{Ned to be precise here. We also use redshifts from redmapper so this statement isn;t quite right}}.  To ensure reasonable 
    \mstar{}-completeness at the high-\mstar{} end we focus on the redshift range $0.3 \leq z \leq 0.5$. 
    %% This is catalog: "dr1_specz_use.fits"

        \alexie{Please rewrite the section below. It would be better to first say that you further supplements with redmapper redshifts. And then simply quote the overall number at the end after making the redshift cut. Need to work on logical flow of text!}.

  In addition to the specz-s mentioned above, we also include objects which have a red-sequence photo-$z$ from the \redm{} catalog within the range $0.2 \leq z \leq 0.5$ .........and need to say one sentance about the accuracy of the red sequence redshifts and why this is tolerable for our work

    \rewrite{For objects without external spec-$z$, we match them with the central galaxies 
    from \redm{} catalog using $2.0^{\arcsec}$ radius. 
    The matched objects with useful red-sequence photo-$z$ ($z_{\lambda}$) are also 
    included in the final sample of bright galaxies with reliable redshift between 
    $0.2 \leq z \leq 0.5$
    (will be referred as \texttt{hscZ}).   From our initial sample, 42696 are at $0.2 \leq z \leq 0.5$.}
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"

    The BOSS and SDSS "legacy" LRG samples provide the majority of spec-$z$ for this work. By comparing with the Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the stellar mass completness of the combined BOSS and SDSS samples. They estimate that the BOSS spec-$z$ is about 80\% complete at \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. The GAMA survey, which partially overlaps with the HSC footprint, supplements our spec-z sample by 14\%. \alexie{and redmapper redshifts add another xx percent.} Based on \citet{Taylor2011} (e.g.\ their Fig.~6), at $z\sim 0.3$, the GAMA 
    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
    $10^{12.0}$\msun at $z\sim 0.5$. We can therfore expect our sample to be roughly stellar-mass complete above \logms{}$\geq 11.5$-$11.6$. This question will be addressed more carefully using the overlap region between HSC and the \texttt{S82-MGC} in Section\ref{ssec:s82}.

@@

    Our study focuses on galaxies which are located at the center of
    their dark matter halos. To limit our sample to central galaxies, we use 
    \texttt{v5.10} of the \redm{}{} cluster 
    catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
    These authors have developed a well-tested red-sequence cluster finder that has been 
    run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
    For each cluster, the catalog provides a photometric redshift estimate $z_{\lambda}$, 
    a richness $\lambda$, and identifies the most likely central
    galaxy (this is the galaxy with the highest central probability value
    $P_{\mathrm{Cen}}$). The \redm{}{} catalog also provides a list of member galaxies for each cluster and associated membership probabilities. Details about the performance of the \redm{}~cluster catalog can be found in 
    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
    Several studies have published calibrations between the \redm{}~richness estimate, 
    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015}; \citealt{Farahi2016}; 
    \citealt{Simet2016}). 
    The results of these studies are in good agreement and indicate that clusters 
    identified by \redm{}~ with $\lambda > 20$ have $\log (M_{200m}/M_{\odot}) \geq 14.0$. 
    Therefore, the \redm{} catalog helps us group massive central galaxies into samples with different average \mhalo{}. \alexie{Here is looks like you are making a cut on pcen. But what about galaxies that are not in these clusters? You do not have a pcen value! So this phrase needs to be rewritten or moved elsewhere.}\rewrite{To select reliable candidates of central galaxies, we only include the ones 
    with high probability of being the central galaxy ($P_{\mathrm{CEN}} \geq 0.7$)}.

    Although the \redm{} catalog provides us a good sample of central galaxies in 
    massive halos, the typical uncertainty of $\lambda$ estimate is still at the
    $\sim 5$-10 level.  
    In addition, due to the depth and resolution of SDSS images, the \redm{} catalog 
    becomes slightly incomplete at lower richness ($\lambda < 40$) at $z > 0.33$.
    To reduce the impact of this effect, we will focus on a sample of central galaxies in halos with 
    $\lambda > 30$. 
    Based on the calibration of \citet{Simet2016}, the $\lambda \geq 30$ sample should
    have halo mass ($M_{200m}$) more massive than $10^{14.2} M_{\odot}$. We have checked that none of our results depend on this choice of the $\lambda$ boundary.

@@

%           We compre the \mstar{} volume-density distributions of 
%      	  \rbcg{} (red) and \nbcg{} (black) galaxies using stellar mass based on 
%          \mcmodel{} (dash) and \mtot{} (solid) to highlight the increase of \mstar{}
%          due to different methods.  
%          Here we also show the volume-density distributions of the \texttt{S82-MGC} 
%          galaxies (green) to evaluate the \mstar{}-completeness. 
%          The vertical line highlight \logms{}$=11.6$ before correcting the \mstar{} using
%          total luminosity from 1-D profile.~~

@@

    \alexie{This section can be synthesized and condensed. Try to be more succinct!}

    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
    the \mhalo{} of \logms{}$ > 11.0$ galaxies has a large scatter at fixed \mstar{}. This means that our sample of massive galaxies spans a wide range of halos masses. We use the \redm{} catalog to separate our sample into two samples with halos masses above and below \logmh{}$<14.0$ \alexie{14.2 no?}.

@@

   We match the \texttt{hscZ} sample with the massive central galaxies of 
    \redm{} clusters with $\lambda \geq 20$ \alexie{20 or 30... confusing here} and $P_{\mathrm{0.7}} \geq 0.7$ using 
    $1.0^{\arcsec}$ radius \alexie{mathcing radius not important}.

     \alexie{confusing paragraph. The remapper redshift accuracy should be moved to the specz section. Why do we care about the number above 0.3? I'd remove those kind of details, they just make the reader confused.}

    \rewrite{This step finds 375 matched galaxies at $0.2 \leq z \leq 0.5$ 
    (among them 282 are at $0.3 \leq z \leq 0.5$).  
    We will refer these \textbf{central galaxies in more massive halos} as \rbcg{} 
    sample from now on.
    A small fraction of \redm{} centrals within the HSC footprints are missing  
    due to severe contamination from optical artifacts or bright stars.
    Spec-$z$ is not available for 67 (17.9\%) galaxies in the sample, but their 
    $z_{\lambda}$ should be very accurate (median $|z_{\lambda} - z_{\mathrm{Spec}}|$ is 
    about 0.01 for the ones with spec-$z$).
    The median richness ($\lambda$) of these clusters is $\sim 32$, corresponding to 
    halo mass of $M_{200m}\sim 1.7\times 10^{14} h^{-1} M_{\odot}$. 
    Among these central galaxies, 222 are in clusters with $\lambda \geq 30$. 
    When focusing on this subsample, the median richness is $\sim 41$, corresponding 
    to halos with $M_{200m} \sim 2.2\times 10^{14} h^{-1} M_{\odot}$. 
    Meanwhile, only 15\% of \rbcg{} sample lives in clusters with $\lambda \geq 50$
    ($M_{200m} \sim 3.0\times 10^{14} h^{-1} M_{\odot}$).   
    Therefore, the current \rbcg{} sample is not dominated by very massive clusters 
    with \mhalo{}$>10^{15} M_{\odot}$.  }
    %% Saved as "dr1_redbcg_use_sed5b.fits"

    \rewrite{Assuming that the \redm{} catalog correctly identifies all halos with 
    $M_{200m}\sim 1.0\times 10^{14} h^{-1} M_{\odot}$ in the current footprint,
    the unmatched massive galaxies from the above step should be dominated by central 
    galaxies of less massive halos and massive satellites galaxies.  
    \update{
    To select a purer sample of massive centrals in $M_{200m}<10^{14} h^{-1} M_{\odot}$
    halos, we identify and remove all galaxies within a cylinder region around the 
    the central galaxies in \redm{} catalog.
    We choose to use the $R_{200m}$ as the radius of the cylinder. 
    For each cluster, we convert the richness estimates into $M_{200m}$ using the 
    calibration in \citep{Simet2016}, then estimate the $R_{200m}$ using $M_{200m}$
    and the mass-concentration relation in \citep{Diemer2015}. 
    For the thickness of the cylinder, we use twice the uncertainty of the photometric 
    redshift error of each cluster.  
    At $0.3 < z < 0.5$, such uncertainty is between 0.015 to 0.025, which are more than 
    enough to exclude cluster member.}}
    % TODO: The actual number waits to be updated}

    %\alexie{This is a rather strange procedure, I think we need to change it (referee and readers will complain!). What we really want to do is to remove any galaxies that have $r<R200$ in projection (from the galaxy with the highest value of Pcen) and remove galaxies within some deltaz of the cluster redshift. The cluster redshift is more well determined than the redshift estiamte of any cluster member. In short, what we are doing here is cutting out a cylindar arond the most likley BCG. The deltaz value can be motivated by the cluster redshift uncertainty from the redmapper papers. The only remaining question is then what radius to use around clusters. To get that number here is what we need to do. 1) Start with Eq 12 and Table 3 in Simet et al. For each cluster, assign a value of M200m (halo mass defined as 200 time background) to each cluster. 3) we then need to estimate the cluster radius R200m (or R200b, same thing). To do this, we need to use a mass-concentration relation. I'm pretty sure there is an easy command to do this in Python using the python package "colossus" by bendikt diemer. Download it and see if youc an get it to work. If it doens't look obvious after 30 min, I can do it on my end using my own code. But good for you to know how to do this. We can simply use the mass-concentration realtion from Benedikts work. 4) Now for every cluster you have R200m. And you define the low halo mass central sample as ones that are not within any cylindar around any cluster. Sorry, I know this might mean re-doing everything.....let's discuss by Skype if this is a major issue.}

    However, we should note that the \nbcg{} sample at this stage spans a large range
    in \mstar{}, extending towards \logms{}$<10^{11}$.  
    Therefore, we should expect contamination from satellites in \logmh{}$< 14.0$ halos
    at certain degree.  
    Later, after we update the total \mstar{} of them, we will mainly focus on the 
    \nbcg{} galaxies at high mass end, especially the ones at \logms{}$ > 11.5$. 
    Based on observational constraints (e.g. \citealt{vanUitert2016}), we can neglect 
    satellite contamination at such high \mstar{} range. 
    %% Saved as "dr1_nonbcg_use_sed5b.fits"

@@

    To estimate the total luminosity of massive galaxies, and measure their 
    one-dimensional stellar mass density (\mden{}) profiles, we perform elliptical 
    isophotes fitting using the IRAF \texttt{Ellipse} algorithm (Jedrzejewski 1987).  
    Compared to the popular two-dimensional model fitting method, the isophote fitting
    approach is insensitive to the choice of a model (one versus two sersics for example), the number of components, 
    and the initial guesses of free parameters. It is also less affected by uncertainties related to background subtraction. This is particularly important for the massive ellipticals in our sample. Massive ETGs imaged at the depth of HSC are not well modeled by simple models such as the de~Vaucouleurs model or a single \ser component model. These models will fail to simultaneously capture the profile in both the inner and the outter region and these models also cannot account for any radial variations in ellipticity and position angle. In principle, massive galaxies can still be described using more complex 
    models (e.g \citealt{Huang2013a}; \citealt{Huang2013b}) but these multi model fits are quite sensitive to the background subtraction. For this paper, we opt to for the model independent 1-D approach and we will only study galaxies in the radial range where we are not sensitive to either the PSF ($r<5$ kpc) or the background subtraction ($r>100$ kpc).

>>>>

    The Subaru Strategic Program (SSP, \citealt{MiyazakiInPrep}) makes use of the new 
    prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
    8.2-m Subaru telescope at Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover $\sim 1400$ deg$^2$ in 5
    broad bands (\textit{g r i z Y}) to a limting depth of $r \sim 26$ mag in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    $\sim 100$square of degree in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

@@

    The full details of the HSC data processing can be found in \citet{BoschInPrep}
    and are briefly summarized here. 
    The HSC SSP data are processed with \texttt{hscPipe 4.0.1}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC. 
    \texttt{hscPipe} first performs a number of tasks at the single exposure level 
    (bias subtraction, flat fielding, background modeling, object detection and 
    measurements). 
    Astrometric and photometric calibrations are performed at the single exposure level. 
    \texttt{hscPipe} then warps different exposures on to a common World Coordinate 
    System (WCS) and combines them into coadded images. 
    At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
    photometric calibration using stars that are common among exposures.

    The pixel scale of the combined images is $0.168^{\arcsec}$. 
    Photometric calibration is based on data from the Panoramic Survey Telescope 
    and Rapid Response System (Pan-STARRS) 1 imaging survey 
    (\citealt{Schlafly2012}, \citealt{Tonry2012}, \citealt{Magnier2013}). 
    To achieve consistent deblending and photometry across all bands, \texttt{hscPipe} 
    performs multi-band post-processing at the coadd level. 
    First, \texttt{hscPipe} performs object detection on coadd images in each band 
    independently and records the flux peak and the above-threshold region 
    (referred as a ``footprint'') for each source. 
    Next, ``footprints'' and peaks from different bands are merged together before     
    performing deblending and measurements. 
    Finally, \texttt{hscPipe} selects a reference band for each object based on the 
    $S/N$ in different bands (for most galaxies in this work, the reference band is 
    the $i$-band). 
    After fixing the centroids, shape, and other non-amplitude parameters of each 
    object in this reference catalog, \texttt{hscPipe} perform forced photometry 
    on the coadd image in each band. 
    This forced photometry approach is optimized to yield accurate galaxy colors.

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
    that is similar to SDSS (\citealt{BoschInPrep}). 
    However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
    means that it can accurately measure both the \textit{fluxes and colors of galaxies}. 
    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
    The performance of this algorithm has been tested using synthetic objects 
    (\citealt{SynPipeInPrep}), and the results indicate that, generally speaking, 
    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of 
    massive ETGs with extended stellar distributions. 
    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
    at the depth of the HSC survey. 
    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
    large ETGs where satellites and background galaxies often blend with the low surface 
    brightness stellar envelope is a challenging problem. 
    The deblending method implemented by the \texttt{hscPipe} currently tends to 
    ``over-deblend'' the outskirts of bright galaxies and leads to un 
    under-estimation of the the total flux of massive ETGs (more discussion in 
    \citealt{BoschInPrep}).  
    For these reasons, our results will be based on custom developed code to measure 
    the luminosities and stellar masses of massive galaxies. 
    We use the HSC \texttt{hscPipe} photometry for two purposes: 
    1) to perform a first broad sample selection, and 2) to estimate the average 
    color of massive galaxies.

@@

    We begin by using a broad luminosity cut to select an initial sample of massive 
    galaxies at $z < 0.5$ from the HSC photometric catalog. 
    Based on Leauthaud\etal~(2016), galaxies with \logms{}$\geq 11.5$ mostly have 
    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. 
    We therefore select our initial sample to be brighter than 
    $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect the insignificant 
    differences between the response curves of SDSS-$i$ and HSC-$i$ filters} 
    and also limit our sample to regions that have reached the required depth of 
    the \texttt{WIDE} survey in $i$-band.
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

    We further select extended objects with no deblending errors, with well defined 
    centroids, and with \texttt{cModel} magnitudes in all five bands. 
    After removing objects that have pixels affected by saturation, cosmic-rays, or 
    other optical artifacts\footnote{each criterion removes less than 8\% of the 
    entire sample}
    %% Alexie: Actually, 8 percent is not small if we want to consider the number 
    %%         densities. Let's re-evaluate the impact of these cuts for the 16B 
    %%         data with FDFC}. 
    This sample corresponds to 1760845 galaxies and will be referred as \texttt{hscPho}. 
    %% Saved as "dr1_wide_galaxy_hscPho.fits"

    Here we limit our study to the very high-\mstar{} end where the majority of galaxies 
    have either a spectroscopic redshift or a robust red-sequence photo-$z$ from the 
    \redm{} catalog (see Section \ref{ssec:redmapper}).  
    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
    team\footnote{It is created by matching HSC objects with all publicly available 
    spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). The spec-z quality flag from 
    different catalogs are homogenized into a single flag that indicates whether the 
    redshift is secure (\ref{}). 
    We only consider the ones with secure spec-$z$s during the match}.  
    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
    the redshift range $0.3 \leq z \leq 0.5$. 
    %% This is catalog: "dr1_specz_use.fits"

    For objects without external spec-$z$, we match them with the central galaxies 
    from the \redm{} catalog using $2.0^{\arcsec}$ radius. 
    The matched objects with useful red-sequence photo-$z$ ($z_{\lambda}$) are also 
    included in the final sample of bright galaxies with reliable redshift between 
    $0.3 \leq z \leq 0.5$. 
    Comparing with spec-$z$, the accuracy of the red-sequence photo-$z$ is sufficient 
    (typical uncertainty $< 0.05$) for the goal of this work.
    The \redm{} catalog provides additional 133 unique redshifts for massive galaxies 
    in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
    reliable redshift information (will be referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    Among them, the BOSS and SDSS "legacy" LRG samples provide the majority of 
    spec-$z$. 
    By comparing with the Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
    \mstar{} completeness of the combined BOSS and SDSS samples. 
    They estimate that the BOSS spec-$z$ is about 80\% complete at \logms{}$\geq 11.6$ 
    at $0.3 < z < 0.5$. 
    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
    our \texttt{hscZ} sample by 14\%. 
    Based on \citet{Taylor2011} (e.g.\ their Fig.~6), at $z\sim 0.3$, the GAMA 
    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
    $10^{12.0}$\msun at $z\sim 0.5$. 
    We can therefore expect our sample to be roughly \mstar{}-complete above 
    \logms{}$\geq 11.5$-$11.6$. 
    This question will be addressed more carefully using the overlap region between 
    HSC and the \texttt{S82-MGC} in Section\ref{ssec:s82}.

@@

    Our study focuses on galaxies which are located at the center of their dark matter 
    halos. 
    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
    These authors have developed a well-tested red-sequence cluster finder that has 
    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
    For each cluster, the catalog provides estimates of photometric redshift 
    ($z_{\lambda}$) and richness ($\lambda$), and identifies the most likely central
    galaxy (the galaxy with the highest $P_{\mathrm{Cen}}$ value). 
    The \redm{}{} catalog also provides a list of member galaxies for each cluster 
    and associated membership probabilities. 
    Details about the performance of the \redm{}~cluster catalog can be found in 
    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
    Several studies have published calibrations between the \redm{}~richness estimate, 
    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015}; \citealt{Farahi2016}; 
    \citealt{Simet2016}). 
    All these studies consistently found that the \redm{} clusters with $\lambda > 20$ 
    have $\log (M_{200m}/M_{\odot}) \geq 14.0$.
    The \redm{} catalog therefore helps us group massive central galaxies into samples 
    with different average \mhalo{}. 
    The reliable candidates of central galaxies in the \redm{} clusters 
    ($P_{\mathrm{CEN}} \geq 0.7$) form a nice sample of massive central galaxies 
    that live in very massive halos.

    Due to the depth and resolution of the SDSS images, the \redm{} catalog 
    becomes slightly incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
    In addition to that, the typical uncertainty of $\lambda$ estimate ($\sim 5$-10) 
    can not be ignored. 
    To ensure the separation in \mhalo{}, here we only focus on the central galaxies of
    clusters with $\lambda > 30$. 
    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should have halo mass
    ($M_{200m}$) more massive than $10^{14.2} M_{\odot}$. 
    Also, none of the results in this work depend on the choice of the $\lambda$ 
    limit.

@@

@@

    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}),
    the massive galaxies in our sample live in halos that span a wide range of 
    \mhalo{}.
    With the help of the \redm{} catalog, we can broadly separate our sample into two
    groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.

@@

    We match the \texttt{hscZ} sample with the massive central galaxies of 
    \redm{} clusters with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$,
    and find 164 matched galaxies at $0.3 \leq z \leq 0.5$.
    We will refer these \textbf{central galaxies in more massive halos} as the 
    \rbcg{} sample here.
    A small fraction of \redm{} centrals within the HSC footprints is missing  
    due to severe contamination from optical artifacts or bright stars.
    The median $\lambda$ of these clusters is $\sim 41$, corresponding to 
    halo mass of $M_{200m}\sim 2.2\times 10^{14} h^{-1} M_{\odot}$.
    Among them, only 44 of \rbcg{} sample live in clusters with $\lambda \geq 50$
    ($M_{200m} \sim 3.0\times 10^{14} h^{-1} M_{\odot}$), so the \rbcg{} sample is 
    not dominated by extremely massive clusters with \mhalo{}$>10^{15} M_{\odot}$. 
    %% Saved as "dr1_redbcg_use_sed5b.fits"

    To select massive central galaxies in \logmh{}$<14.0$ halos, we identify and 
    remove all galaxies within a cylinder region around each of the central galaxy of 
    all \redm{} clusters.
    We choose to use the $R_{200m}$ as the radius, and twice the uncertainty of the 
    photometric redshift error as the thickness of the cylinder. 
    We convert the $\lambda$ into $M_{200m}$ using the calibration in 
    \citep{Simet2016}, then estimate the $R_{200m}$ with the help of the 
    mass-concentration relation in \citep{Diemer2015}. 
    At $0.3 < z < 0.5$, the uncertainty of photo-$z$ is between 0.015 to 0.025, 
    and is enough to exclude cluster members.
    After removing galaxies in \redm{} clusters, the rest of the massive galaxies 
    in our sample should mainly be the central galaxies of halos with \logmh{}$<14.0$,
    and we will refer these \textbf{central galaxies in less massive halos} as the 
    \nbcg{} sample.
    We should note that the \nbcg{} sample at this stage spans a large range in 
    \mstar{}, and includes contaminations like massive satellites in \logmh{}$< 14.0$ 
    halos.  
    Therefore, after we update the total \mstar{} later, we only focus on the 
    \nbcg{} galaxies at very high-mass end (e.g.~\logms{}$ > 11.5$). 
    According to recent observation (e.g. \citealt{vanUitert2016}), we can neglect 
    satellite contamination at such high \mstar{} range. 
    %% Saved as "dr1_nonbcg_use_sed5b.fits"
    % TODO: The actual number waits to be updated}

    % \alexie{This is a rather strange procedure, I think we need to change it 
    % (referee and readers will complain!). What we really want to do is to remove any
    % galaxies that have $r<R200$ in projection (from the galaxy with the highest value 
    % of Pcen) and remove galaxies within some deltaz of the cluster redshift. 
    % The cluster redshift is more well determined than the redshift estimate of any 
    % cluster member. 
    % In short, what we are doing here is cutting out a cylinder around the most likely 
    % BCG. The deltaz value can be motivated by the cluster redshift uncertainty from 
    % the redmapper papers. The only remaining question is then what radius to use around
    % clusters. To get that number here is what we need to do. 
    % 1) Start with Eq 12 and Table 3 in Simet et al. For each cluster, assign a value 
    % of M200m (halo mass defined as 200 time background) to each cluster. 
    % 3) we then need to estimate the cluster radius R200m (or R200b, same thing). 
    % To do this, we need to use a mass-concentration relation. 
    % I'm pretty sure there is an easy command to do this in Python using the python 
    % package "colossus" by bendikt diemer. 
    % Download it and see if you an get it to work. If it doesn't look obvious after
    % 30 min, I can do it on my end using my own code. But good for you to know how to 
    % do this. We can simply use the mass-concentration relation from Benedikts work. 
    % 4) Now for every cluster you have R200m. And you define the low halo mass central
    % sample as ones that are not within any cylindar around any cluster. 
    % Sorry, I know this might mean re-doing everything.....let's discuss by Skype if 
    % this is a major issue.}

@@

    To estimate the total luminosity of massive galaxies, and measure their 
    one-dimensional stellar mass density (\mden{}) profiles, we perform elliptical 
    isophotes fitting using the IRAF \texttt{Ellipse} algorithm (Jedrzejewski 1987).  
    Compared to the popular two-dimensional model fitting method, the isophote fitting
    approach is insensitive to the choice of model (e.g. de~Vaucouleurs or \ser{} 
    profile), the number of components, and the initial guesses of free parameters. 
    It is also less affected by the background subtraction uncertainty, which is 
    particularly important for the massive ellipticals in our sample.
    Massive ETGs imaged at the depth of HSC are not well modeled by simple models such 
    as the de~Vaucouleurs model or a single \ser component model. 
    These models will fail to simultaneously capture the profile in both the inner and 
    the outer region and these models also cannot account for any radial variations in 
    ellipticity and position angle. 
    In principle, massive galaxies can still be described by more complex 
    models (e.g \citealt{Huang2013a}; \citealt{Huang2013b}), but they are still 
    sensitive to background subtraction and initial values of parameters. 
    For this paper, we opt to for the model-independent 1-D approach and we will only 
    study galaxies in the radial range where we are not sensitive to either the PSF 
    ($r<3-5$ kpc) or the background subtraction ($r>100$ kpc).
